BareTag Tool-Tracker\\ {\footnotesize {Team 3 - University of Massachusetts Amherst Senior Design Project 2025 }}

### 2024-10-19 draft.tex

\author{
    \IEEEauthorblockN{Sean Brown}
    \IEEEauthorblockA{\textit{Computer Engineering} \\
    \textit{Logistics Lead}\\}
    \and
    \IEEEauthorblockN{Connor McGarry}
    \IEEEauthorblockA{\textit{Computer Engineering} \\
    \textit{Hardware Lead}\\}
    \and
    \IEEEauthorblockN{Ken Su}
    \IEEEauthorblockA{\textit{Computer Engineering} \\
    \textit{Budget Lead}\\}
    \and
    \IEEEauthorblockN{Walter Tebbetts}
    \IEEEauthorblockA{\textit{Computer Engineering} \\
    \textit{Software Lead}\\}
    \and
    \IEEEauthorblockN{Professor Jeremy Gummeson}
    \IEEEauthorblockA{\textit{UMass Amherst ECE Faculty} \\
    \textit{Advisor}\\}
}

@@

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

>>>>

\author{\IEEEauthorblockN{Walter Tebbetts}
\textit{CompE}\\
\textit{Software Lead}

\and
\IEEEauthorblockN{Sean Brown}
\textit{CompE}\\
\textit{Logistics Lead}

\and
\IEEEauthorblockN{Ken Su}
\textit{CompE}\\
\textit{Budget Lead}

\and
\IEEEauthorblockN{Connor McGarry}
\textit{CompE}\\
\textit{Hardware Lead}

}

@@

\[ d = \frac{\frac{ToF}{2}}{c} \]
Where $d$ is distance, $ToF$ is time of flight, and $c$ is the speed of light.

\subsection{Tag}

\subsection{Block 2}

\subsection{Block 3}

\subsection{Block 4}
